---
title: "CourseworkPackage_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CourseworkPackage_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
author: 10556321, 10557769
date: "08/01/2020"

---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width=9,
  fig.height=6
)
```

```{r setup, echo=FALSE}
library(PresidentialDebate2012)
```

In this package, there are three major functions:

* prop_plot()

* freq_plot()

* zipf_plot()

In this document, the use of the functions, as well as thier purpose, shall be illustrated.

## prop_plot

```{r prop_plot}
#testwords<-c('word1','word2',....,'wordn')
#prop_plot(testwords)
```
Here is a generic example of how to use the prop_plot function. The usage items are thus:

* First create a vector of words you wish to compare using the function

* Then simply call the function and between the parentheses insert the vector you have created.

```{r prop_plot_example, echo=TRUE}
require(CourseworkPackage)
testwords<-c('jobs','military','china','people')
print(prop_plot(testwords))
```

This produces a plot of the change in proportion of the words in the vector compared with the dialogue recorded over the course of the 2012 U.S Presidential Election debates between then-president Barack Obama and Republican nominee Mitt Romney, moderated by Jim Lehrer, Candy Crowley and Bob Schieffer, with questions from the audience.

## freq_plot

```{r freq_plot,echo=TRUE}
freq_plot()
```

This command shows the 10 most frequent words used by each person throughout the course of the debates.

## zipf_plot

```{r zipf_plot}
zipf_plot()
```

This command produces a plot illustrating Zipf's Law, which states that the most frequently appearing word in a set of words, be it a report or in this case a transcript, appears twice as often as the second most common, three times more than the third most common etc.

